The Astropy Project

### 2017-12-07 main.tex
To make southern hemisphere happy

In the next major release after version 3.0, scheduled for the summer of
2018, the focus will be on optimization of the code and improved
documentation.
To prepare for this release, we are preparing software for testing, evaluating,
and monitoring the performance of the code.
Less functionality may be introduced in this release while the focus will be
primarily on improved performance.

>>>>

In the next major release after version 3.0, scheduled for around
mid-2018, the focus will be on optimization of the code and improved
documentation.
To prepare for this release, we are preparing software for testing, evaluating,
and monitoring the performance of the code.
Less functionality may be introduced in this release while the focus will be
primarily on improved performance.
